A generalization of the Bradley-Terry model for draws in chess

### 2020-09-30 inst/jebo_chess_revision2.tex
typo --   Fisher is not Fischer!

\textcolor{DarkGreen}{It is reasonable to suppose that collusion of
  the type considered here is ``effective'' in the sense that
  noncollusive games are detrimental to future play in a way that
  collusively drawn games are not.  At the end of the tournament,
  Petrosian, Keres and Geller had each played a total of 18
  noncollusive matches while Fisher, Benko and Filip had played a
  total of 26 or 27 (Tal, retiring mid tournament due to illness,
  played only 21).  For each game, we count the noncollusive games
  played up to that point in the match for White and Black.  If, in
  that game, the number of noncollusive games differ by more than 1,
  we posit a ``rest monster'' whose strength helps the player who has
  played fewer noncollusive games.  Observing that the rest monster is
  active in 49 of the 105 games of the tournament, we may consider
  these 49 games and, discarding draws, test whether rested players
  actually win more often than expected; observations are given in
  Table~\ref{restmonsterfisher} .  We reject the null of rested
  players having the same win probability as their more tired
  opponents (one-sided Fisher's exact test, $p\simeq 10^{-4}$).}

>>>>

\textcolor{DarkGreen}{It is reasonable to suppose that collusion of
  the type considered here is ``effective'' in the sense that
  noncollusive games are detrimental to future play in a way that
  collusively drawn games are not.  At the end of the tournament,
  Petrosian, Keres and Geller had each played a total of 18
  noncollusive matches while Fischer, Benko and Filip had played a
  total of 26 or 27 (Tal, retiring mid tournament due to illness,
  played only 21).  For each game, we count the noncollusive games
  played up to that point in the match for White and Black.  If, in
  that game, the number of noncollusive games differ by more than 1,
  we posit a ``rest monster'' whose strength helps the player who has
  played fewer noncollusive games.  Observing that the rest monster is
  active in 49 of the 105 games of the tournament, we may consider
  these 49 games and, discarding draws, test whether rested players
  actually win more often than expected; observations are given in
  Table~\ref{restmonsterfisher} .  We reject the null of rested
  players having the same win probability as their more tired
  opponents (one-sided Fisher's exact test, $p\simeq 10^{-4}$).}
